---
title: "My report"
author: "Lina Maria Serna Higuita"
date: "29 9 2020"
output:
  html_document: 
   theme: lumen
   highlight: kate
   toc: yes
   toc_float: yes
   
   
---

```{r libraries, warning=TRUE, include=FALSE, paged.print=TRUE}
# library(Lina-first-report)
library(ggplot2)

```

## R Markdown

# Tgkkjkhvkhvhjvhjfzfftfzufugkkkkkkkkkkkkkkkkkkkkkkkk
# kojjgjfdtddddddddddddddddddddddddddddddddddddddddddddd
# jjuAQZWZZA
> 1. 
> > 2.

# When you click the **GJÖOGJAGJLKANGLKAJGKNH** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

# ggjnkgnkjangkgkabg

library(tidyverse)

```{r cars, message=TRUE, warning=TRUE}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
